### 2011-02-03 latex/paper.tex
Naplnenie sablonou a zaciatok introduction

\documentclass{ifacconf}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{natbib}

\bibpunct{(}{)}{;}{a}{,}{}

\begin{document}
\begin{frontmatter}
\title{Simulation of 2D physics of hand drawn objects using OpenCV and Box2D}
\author[Bratislava]{Michal Sedlák}
\address[Bratislava]{Faculty of Electrical Engineering and Information Technology, Slovak University of Technology,
Ilkovičova 3, 812 19 Bratislava, Slovakia
\\
(e-mail: michal.sedlak@stuba.sk)}
\begin{abstract}
%TODO Napisat abstrakt

\end{abstract}
\begin{keyword}
Maximum 5 keywords.
\end{keyword}
\end{frontmatter}

\section{Introduction}
This paper describes applying of Newtonian physics to hand drawn objects recognized in image from camera. Simulation of physics is used in many modern applications. You can find in implementations used by 3D drawing and animation programs, more complex used in game engines or exact and precise simulation in CAE programs. Paper describes process of animation of hand drawn object, from a capturing phase, over recognition of the objects, interpretation objects in physical engine, to animation of such objects. This approach can be applied in education of physics at elementary schools, in interactive blackboards, or in games.

Figure~\ref{fig:song} demonstrates placement of figures. Place figures at
the top or bottom of a column wherever possible, as close as possible
to the first references to the in the paper. Restrict them to
single-column width please.

\subsection{Equations}
Center equations and place the numbers on the right as follows:
\begin{equation}
a^2+b^2=c^2
\end{equation}

\begin{figure}
\vspace*{3cm}
\caption{Example of a figure, to demonstrate the effect of
  long captions which run onto a second line}
\label{fig:song}
\end{figure}

\section{Transfer of your files to PC'11}

If it is not possible to send the electronic version of the paper and
summary, the paper version (two originals, not a photocopy) of your
full paper and abstract should be sent to the conference secretariat
by registered mail or courier service.

The electronic version of your full paper and abstract are to be sent
via web page of the conference. The registration process makes use of
an internet database system and consists of three consecutive steps
(detailed description and help will be available on-line):
\begin{enumerate}
\item Author registration to obtain author's PIN. Each author or
  participant of the conference will receive a unique number and
  password. This number will identify the author when submitting the
  paper, creating invoice, etc. Persons that participated at past PC have
  their PIN already registered.  Based on PIN and password, the
  authors are be able to update or modify their coordinates (address,
  email, affiliation, etc) at any time. This information is secured by
  a password that can be send to authors again if forgotten.
\item Paper registration. Each accepted paper with unique ID will be
  added to the database via internet form. This contains a field where
  files can be attached and it will be sent to organisers together
  with other information on the form. Only the respective authors will
  be able to upload the title, paper, and abstract. Also, they will be
  able to modify this information later.
\item Invoice generation. The participants of the conference will
  fill in the web form and an invoice will automatically be generated
  for them. 
\end{enumerate}

The name of your file can be arbitrary.

Since the final electronic version will be the PDF format we prefer to
receive PDF files. The authors are encouraged to use hypertext
capabilities of the Acrobat software.  Before sending the PDF files to
the please test viewing and printing your file with Adobe Acrobat
Reader (Version 5.0). If you send the PS file, test it with
Ghostview.

Important note: Please do not generate PDF with version 1.5 or higher.
The Adobe company provides Reader for this PDF version only for some
computer platforms and some people may not be able to read your
documents. This is for example case of Acrobat 6. Check its settings
and choose optimisations for version 1.4.

If your file exceeds the size of 10 MB, contact the organisers as this
is the limit of the web server.

The list of references must be at the end of the paper. When
referring to them in the text, type the corresponding reference
as \cite{AbTaRu:54},  \cite{Abl:56},
\cite{Keo:58}.
References should be given in the standard style as below.

\section*{Acknowledgments}
The work was supported by a grant (No. NIL-I-007-d) from Iceland, Liechtenstein 
and Norway through the EEA Financial Mechanism and the Norwegian Financial 
Mechanism. This project is also co-financed from the state budget of the Slovak Republic..

%If you use BibTeX comment the second line, if not comment the first line
\bibliography{pcbib}
%\input{paper.bbl}

\end{document}

### 2011-02-04 latex/paper.tex
Vytvorenie eclipse projektu
dopisana introduction a opencv cast

@@
 \bibpunct{(}{)}{;}{a}{,}{}
+
+\usepackage{color}
+\usepackage{listings}
+\lstset{ %
+language=Python,                % choose the language of the code
+basicstyle=\footnotesize,       % the size of the fonts that are used for the code
+numbers=left,                   % where to put the line-numbers
+numberstyle=\tiny,
+xleftmargin= 10pt,
+stepnumber=1,                   % the step between two line-numbers. If it is 1 each line will be numbered
+numbersep=5pt,                  % how far the line-numbers are from the code
+backgroundcolor=\color{white},  % choose the background color. You must add \usepackage{color}
+showspaces=false,               % show spaces adding particular underscores
+showstringspaces=false,         % underline spaces within strings
+showtabs=false,                 % show tabs within strings adding particular underscores
+frame=none,   		% adds a frame around the code
+tabsize=2,  		% sets default tabsize to 2 spaces
+captionpos=b,   		% sets the caption-position to bottom
+breaklines=true,    	% sets automatic line breaking
+breakatwhitespace=false,    % sets if automatic breaks should only happen at whitespace
+escapeinside={\%}{)}          % if you want to add a comment within your code
+}
 
@@
 \section{Introduction}
-This paper describes applying of Newtonian physics to hand drawn objects recognized in image from camera.
-Simulation of physics is used in many modern applications.
-You can find in implementations used by 3D drawing and animation programs, more complex used in game engines or exact and precise simulation in CAE programs.
-Paper describes process of animation of hand drawn object, from a capturing phase, over recognition of the objects, interpretation objects in physical engine, to animation of such objects.
-This approach can be applied in education of physics at elementary schools, in interactive blackboards, or in games.
+This paper describes applying of Newtonian physics to hand drawn objects
+recognized in image from camera. Simulation of physics is used in many modern
+applications. You can find in implementations used by 3D drawing and animation
+programs, more complex used in game engines or exact and precise simulation in
+CAE programs. Paper describes process of animation of hand drawn object, from a
+capturing phase, over recognition of the objects, interpretation objects in
+physical engine, to animation of such objects. This approach can be applied in
+education of physics at elementary schools, with interactive blackboards, or in
+computer games.
 
-Figure~\ref{fig:song} demonstrates placement of figures. Place figures at
-the top or bottom of a column wherever possible, as close as possible
-to the first references to the in the paper. Restrict them to
-single-column width please.
+\section{Object detection and Open Computer Vision library}
+To apply a physics to hand drawn objects we need to identify and isolate
+objects from image. We have used a web camera as a source and Open Computer
+Vision library as processing tool of the images.
 
-\subsection{Equations}
-Center equations and place the numbers on the right as follows:
-\begin{equation}
-a^2+b^2=c^2
-\end{equation}
+\subsection{OpenCV}
+In regards the book of \cite{OpenCV} OpenCV  is a library for open source
+programming funtions for real time computer vision, with more than five hundred
+optimized algorithms. It can be used with C++, C and Python. We chose Python for
+implementation in our application.
 
-\begin{figure}
-\vspace*{3cm}
-\caption{Example of a figure, to demonstrate the effect of
-  long captions which run onto a second line}
-\label{fig:song}
-\end{figure}
+Simple image capture is shown in Listing \ref{Capture}.
+\begin{lstlisting}[caption=Query image frame from web camera, label=Capture]
+self.camera = cv.CaptureFromCAM(-1) %\label{Capture:init})
+self.image = cv.QueryFrame(self.camera) %\label{Capture:query})
+self.DetectOutline(self.image)
+\end{lstlisting}
+In line \ref{Capture:init} of listing \ref{Capture} we initialize our web
+camera. In variable camera is allocated and initialized object that can query
+camera for new image. Then as we see in \ref{Capture:query} we can get the
+image from camera and store it in the variable named image. Now when we have
+image data stoerd in the variable, we can process data to find outlines.
+\begin{lstlisting}[caption=Outline detection, label=Detect]
+def DetectOutline(self, image):
+  image_size = cv.GetSize(image)
+  grayscale = cv.CreateImage(image_size, 8, 1)	%\label{Detect:grayscale})
+  cv.CvtColor(image, grayscale, cv.CV_BGR2GRAY)
+  cv.EqualizeHist(grayscale, grayscale)	%\label{Detect:equalize})
+  storage = cv.CreateMemStorage(0)
+  cv.Threshold(grayscale, grayscale, 50, 255, cv.CV_THRESH_BINARY) %\label{Detect:threshold})
+  self.contours = cv.FindContours(grayscale, %\label{Detect:contours})
+    cv.CreateMemStorage(),
+    cv.CV_RETR_TREE,
+    cv.CV_CHAIN_APPROX_SIMPLE)
+  if len(self.contours) > 0:
+    self.contours = cv.ApproxPoly (self.contours, %\label{Detect:approx})
+      storage,
+      cv.CV_POLY_APPROX_DP,
+      1.5,
+      1)
+  return self.contours
+\end{lstlisting}
+In function in Listing \ref{Detect} is shown how to find outlines of objects in
+image. We convert image to gray scale as seen on line \ref{Detect:grayscale}.
+Then we run histogram equalization (line: \ref{Detect:equalize}).
+Equalization makes objects better visible and gives better output for
+thresholding (line: \ref{Detect:threshold}) which makes black and white image
+prepared for outline detection (line: \ref{Detect:contours}).
 
-\section{Transfer of your files to PC'11}
+After outline detection we have tree of contours stored in the variable
+self.contours. These trees are iterable objects sorted from outer to inner
+outline connected by property h\_next and v\_next that we will describe in
+paragraph about creation of objects from outlines.
 
-If it is not possible to send the electronic version of the paper and
-summary, the paper version (two originals, not a photocopy) of your
-full paper and abstract should be sent to the conference secretariat
-by registered mail or courier service.
+Countour can be very complicated and consist of thousands of points, which could
+cause too complicated objects. Complicated objects is time demanding to
+simulate, that is why we use polynomial approximation of the contour points.
+(line:~\ref{Detect:approx}).
 
-The electronic version of your full paper and abstract are to be sent
-via web page of the conference. The registration process makes use of
-an internet database system and consists of three consecutive steps
-(detailed description and help will be available on-line):
-\begin{enumerate}
-\item Author registration to obtain author's PIN. Each author or
-  participant of the conference will receive a unique number and
-  password. This number will identify the author when submitting the
-  paper, creating invoice, etc. Persons that participated at past PC have
-  their PIN already registered.  Based on PIN and password, the
-  authors are be able to update or modify their coordinates (address,
-  email, affiliation, etc) at any time. This information is secured by
-  a password that can be send to authors again if forgotten.
-\item Paper registration. Each accepted paper with unique ID will be
-  added to the database via internet form. This contains a field where
-  files can be attached and it will be sent to organisers together
-  with other information on the form. Only the respective authors will
-  be able to upload the title, paper, and abstract. Also, they will be
-  able to modify this information later.
-\item Invoice generation. The participants of the conference will
-  fill in the web form and an invoice will automatically be generated
-  for them. 
-\end{enumerate}
+\section{Physics simulation in Box2D}
 
-The name of your file can be arbitrary.
+\subsection{World}
+\subsection{Gravity}
+\subsection{Objects}
+\subsubsection{Body}
+\subsubsection{Shapes and collisions}
+\subsection{Tesselation}
 
-Since the final electronic version will be the PDF format we prefer to
-receive PDF files. The authors are encouraged to use hypertext
-capabilities of the Acrobat software.  Before sending the PDF files to
-the please test viewing and printing your file with Adobe Acrobat
-Reader (Version 5.0). If you send the PS file, test it with
-Ghostview.
-
-Important note: Please do not generate PDF with version 1.5 or higher.
-The Adobe company provides Reader for this PDF version only for some
-computer platforms and some people may not be able to read your
-documents. This is for example case of Acrobat 6. Check its settings
-and choose optimisations for version 1.4.
-
-If your file exceeds the size of 10 MB, contact the organisers as this
-is the limit of the web server.
-
-The list of references must be at the end of the paper. When
-referring to them in the text, type the corresponding reference
-as \cite{AbTaRu:54},  \cite{Abl:56},
-\cite{Keo:58}.
-References should be given in the standard style as below.
+\section{Future work}
+Identifikacia objektov
+Sledovanie objektov a morfing
+Interakcia hybucich sa objektov zachytenych kamerov s Box2D reprezentaciou
 

### 2011-02-06 latex/paper.tex
dopisane opencv zacate box2d

@@
 \lstset{ %
-language=Python,                % choose the language of the code
-basicstyle=\footnotesize,       % the size of the fonts that are used for the code
-numbers=left,                   % where to put the line-numbers
+language=Python, 
+basicstyle=\footnotesize,
+numbers=left,
 numberstyle=\tiny,
 xleftmargin= 10pt,
-stepnumber=1,                   % the step between two line-numbers. If it is 1 each line will be numbered
-numbersep=5pt,                  % how far the line-numbers are from the code
-backgroundcolor=\color{white},  % choose the background color. You must add \usepackage{color}
-showspaces=false,               % show spaces adding particular underscores
-showstringspaces=false,         % underline spaces within strings
-showtabs=false,                 % show tabs within strings adding particular underscores
-frame=none,   		% adds a frame around the code
-tabsize=2,  		% sets default tabsize to 2 spaces
-captionpos=b,   		% sets the caption-position to bottom
-breaklines=true,    	% sets automatic line breaking
-breakatwhitespace=false,    % sets if automatic breaks should only happen at whitespace
-escapeinside={\%}{)}          % if you want to add a comment within your code
+stepnumber=1,
+numbersep=5pt,
+backgroundcolor=\color{white}, 
+showspaces=false,
+showstringspaces=false,
+showtabs=false,
+frame=none,
+tabsize=2,
+captionpos=b,
+breaklines=true,
+breakatwhitespace=false,
+escapeinside={\%}{)}
 }
@@
 \author[Bratislava]{Michal Sedlák}
-\address[Bratislava]{Faculty of Electrical Engineering and Information Technology, Slovak University of Technology,
-Ilkovičova 3, 812 19 Bratislava, Slovakia
+\address[Bratislava]{Faculty of Electrical Engineering and Information
+Technology, Slovak University of Technology, Ilkovičova 3, 812 19 Bratislava,
+Slovakia
 \\
@@
 In regards the book of \cite{OpenCV} OpenCV  is a library for open source
-programming funtions for real time computer vision, with more than five hundred
+programming functions for real time computer vision, with more than five hundred
 optimized algorithms. It can be used with C++, C and Python. We chose Python for
@@
 image from camera and store it in the variable named image. Now when we have
-image data stoerd in the variable, we can process data to find outlines.
+image data stored in the variable, we can process data to find outlines.
 \begin{lstlisting}[caption=Outline detection, label=Detect]
@@
 prepared for outline detection (line: \ref{Detect:contours}).
-
+%TODO Doplnit obrazok s normalizaciou histogramu
+%TODO Doplnit obrazok s thresholdom
 After outline detection we have tree of contours stored in the variable
@@
 
-Countour can be very complicated and consist of thousands of points, which could
-cause too complicated objects. Complicated objects is time demanding to
-simulate, that is why we use polynomial approximation of the contour points.
+Contour can be very complicated and consist of thousands of points, which could
+cause too complicated objects. It is time demanding to simulate complicated
+objects, that is why we use polynomial approximation of the contour points.
 (line:~\ref{Detect:approx}).
 
+Now we have all outlines stored in the outline tree structure, so we can create
+objects and apply a physics.
+%TODO Doplnit obrazok so zvyraznenymi outlineami
+
 \section{Physics simulation in Box2D}
+There is lot of physics engines that can be used for simulation of physics.
+Because we wanted to simulate physics only in 2D we could, code our own
+implementation of physics, or use one of commercial or open source engines. We
+chose Box2D[\cite{GameEngines}], which is open source 2D physiscs engine with
+posibility to simulate rigid body objects and their collisions.
+\subsection{World}
+To create physics simulation we need to create world. World is object that
+manages memory, objects and simulation. Creation of world is shown in Listing
+\ref{World}:
+\begin{lstlisting}[caption=Creation of Box2D world,label=World]
+self.worldAABB=box2d.b2AABB()
+self.worldAABB.lowerBound = (-100.0, -100.0) %\label{World:lower})
+self.worldAABB.upperBound = ( 600.0, 600.0)	%\label{World:upper})
+gravity = (0.0, -10.0) %\label{World:gravity})
 
-\subsection{World}
-\subsection{Gravity}
+doSleep = True %\label{World:sleep})
+self.world = box2d.b2World(self.worldAABB, gravity, doSleep)
+\end{lstlisting}
+First we have to create boundaries of the world. We define them as vectors from
+bottom left (line: \ref{World:lower}) to top right (line:
+\ref{World:upper}). Objects have to be inside the boudaries, when an object
+touch the boundary it gets stuck. Then we define gravity vector (line:
+\ref{World:gravity}). The last thing before creation of the world we allow
+objects to sleep(line: \ref{World:sleep}). Object that are not moving fall
+asleep, then are ignored by the engine. Last line of Listing \ref{World} creates
+the world.
+
+When we have world created we are ready to create objects from outlines.
 \subsection{Objects}
-\subsubsection{Body}
-\subsubsection{Shapes and collisions}
+Every object that is simulated in Box2D consists of body and shapes.
+\subsubsection{Bodies, shapes and collisions}
+Bodies are skelet used by shapes. One body can contain more shapes, but one
+shape could be attached to only one body. Box2d is rigid body
+physics engine, that mean that shapes attached to body can not move against
+other, or body.
 \subsection{Tesselation}
+Box2D supports only collisions between convex objects. That is why we need to
+breake outlines to convex polygons. There is more ways how to break concave
+objects. We chose Seidel's Triangulation Algorithm implemented by poly2tri
+Python library
+%TODO asi iny algorytmus
+%TODO pridat referenciu na poly2tri
 
+\subsection{Implementation}
+%TODO dat sem zdrojovy kod a popisat ho
 \section{Future work}
@@
 and Norway through the EEA Financial Mechanism and the Norwegian Financial 
-Mechanism. This project is also co-financed from the state budget of the Slovak Republic..
+Mechanism. This project is also co-financed from the state budget of the Slovak
+Republic..
 

### 2011-02-07 latex/paper.tex
dalsia kapitola rozpisana

@@
 \usepackage[utf8]{inputenc}
+\usepackage{url}
 \usepackage{natbib}
@@
 chose Box2D[\cite{GameEngines}], which is open source 2D physiscs engine with
-posibility to simulate rigid body objects and their collisions.
+possibility to simulate rigid body objects and their collisions.
 \subsection{World}
@@
 bottom left (line: \ref{World:lower}) to top right (line:
-\ref{World:upper}). Objects have to be inside the boudaries, when an object
+\ref{World:upper}). Objects have to be inside the boundaries, when an object
 touch the boundary it gets stuck. Then we define gravity vector (line:
@@
 
-When we have world created we are ready to create objects from outlines.
+World is created and we are ready to create objects from outlines.
 \subsection{Objects}
-Every object that is simulated in Box2D consists of body and shapes.
+Every object that is simulated in Box2D consists of body and shapes. Our objects
+are described by the contour tree. To create objects we need to iterate contour
+tree, find contours that belongs to together and create objects for these
+contours.
+\subsubsection{Contour tree}
+Contour tree is object in which are stored points of each contour. Contours are
+connected by functions returning reference to other contours with h\_next() and
+v\_next(). h\_next() is referencing to deeper contour, and v\_next is
+referencing to another object contour. To iterate over all contours we have
+created recursive function shown in Listing: \ref{CreateObjects}.
+\begin{lstlisting}[label=CreateObjects,caption=Function to iterate through
+contour tree]
+def CreateObjectsFromCountours(self,cont,h=0,v=0):
+  if v>0:	%\label{CreateObjects:depth})
+    density = 10.0 %\label{CreateObjects:density10})
+  else:
+    density = 0 %\label{CreateObjects:density0})
+  if len(cont)>8:
+    self.CreateObject(cont,h,v)
+
+  if cont.v_next():
+    v += 1
+    self.CreateObjectsFromCountours(cont.v_next(),h,v)
+    v -= 1
+
+  if cont.h_next():
+    h += 1
+    self.CreateObjectsFromCountours(cont.h_next(),h,v)
+\end{lstlisting}
+We iterate through contour tree. First level is outer contour of the image
+(Line: \ref{CreateObjects:depth}), because we do not want the outer contour to
+move, we set it as static byt setting density to 0 (Line:
+\ref{CreateObjects:density0}). Every other contour is dynamic body with density
+set to 10 (Line: \ref{CreateObjects:density10}).
+
+When we know what type of object we will create, we can create bodies and
+shapes for our contours.
 \subsubsection{Bodies, shapes and collisions}
-Bodies are skelet used by shapes. One body can contain more shapes, but one
-shape could be attached to only one body. Box2d is rigid body
-physics engine, that mean that shapes attached to body can not move against
-other, or body.
+Bodies are backbone used by shapes. One body can contain more shapes, but one
+shape could be attached to only one body. Box2d is rigid body physics engine,
+that mean that shapes attached to body can not move against other, or body. Body
+have position and velocity. Forces, torques and impulses can be applied to body
+[\cite{Box2DManual}].  Bodies just hold the shapes. Shapes are elements that
+collide together.
+
+Listing \ref{Objects} shows how to create object from outer contour: 
+\begin{lstlisting}[name=Objects,label=Objects,caption=Creation of object from
+outer contour]
+def CreateObject(self, cont, h,v):
+  contM = []
+  for point in cont:
+    x = point[0]/30.0	%\label{Objects:scaling})
+    y = point[1]/30.0
+    contM.append((x,y))
+
+  bd=box2d.b2BodyDef() %\label{Objects:CreateBody})
+  bd.position = ( 0.0, 0.0 )
+
+  edgeDef=box2d.b2EdgeChainDef() %\label{Objects:CreateChain})
+  edgeDef.setVertices(contM) %\label{Objects:AssignVertices})
+
+  if v==0:
+    body = self.world.CreateBody(bd)
+    try:
+      self.contourBodies.append(body)
+    except:
+      self.contourBodies = [body] %\label{Objects:CountourBodies})
+      body.CreateShape(edgeDef) %\label{Objects:AttachShape})
+\end{lstlisting}
+Image size is measured in pixels and Box2D units are kilograms, meters,
+and seconds (KMS) we should scale images coordinates to fit in 0.1m to
+10m. In that scale is performance of Box2D the best. We are doing it by
+dividing of value of pixel coordinates by 30.0 (Line: \ref{Objects:scaling})
+
+Then we create a body definition that will represent our contour(Line:
+\ref{Objects:CreateBody}) and set up it initial possition in next line.
+
+After that we create shape of body as chain of edges (Line:
+\ref{Objects:CreateChain}) and assign the array of vertices to it (Line:
+\ref{Objects:AssignVertices}). Edges are special type of shapes that have no
+mass, is represented as line betven vertices that collide with other non-edge
+objects. Edges are easy to create because they do not have to be concave unlike
+polygons.
+
+At last we attach this shape to created body \ref{Objects:AttachShape}. Because
+Box2D does not keep track about body definitions, we have to store bodies in to
+array for later use\ref{Objects:CountourBodies}.
+
+Listing of the function CreateObject() continous in Listing \ref{Objects}. This
+part of function creates dynamic objects inside the outer contour.
+\begin{lstlisting}[name=Objects,firstnumber=auto,label=Objects,caption=Creation of objecs] if v == 1: try:
+      body = self.objectBodies[h]
+    except:
+      body = self.world.CreateBody(bd)
+      self.objectBodies[h] = body
+    polyline = []
+    for (x,y) in cont:
+      polyline.append(p2t.Point(x,y))
+    cdt = p2t.CDT(polyline)
+    triangles = cdt.triangulate()
+    for t in triangles:
+      x1 = t.a.x/30.0
+      y1 = t.a.y/30.0
+      x2 = t.b.x/30.0
+      y2 = t.b.y/30.0
+      x3 = t.c.x/30.0
+      y3 = t.c.y/30.0
+      if math.hypot(x2-x1,y2-y1)<0.1:
+        x2 = x2 + math.copysign(0.1, x2-x1)
+        y2 = y2 + math.copysign(0.1, y2-y1)
+        print "kratky vektor"
+      if math.hypot(x3-x2,y3-y2)<0.1:
+        x3 = x3 + math.copysign(0.1, x3-x2)
+        y3 = y3 + math.copysign(0.1, y3-y2)
+        print "kratky vektor"
+      if math.hypot(x1-x3,y1-y3)<0.1:
+        x1 = x1 + math.copysign(0.1, x1-x3)
+        y1 = y1 + math.copysign(0.1, y1-y3)
+        print "kratky vektor"
+      poly=box2d.b2PolygonDef()
+      poly.setVertices(((x1, y1), (x2, y2), (x3, y3)))
+      poly.density = 1.0
+      poly.restitution = 0.0
+      poly.friction = 0.0
+      body.CreateShape(poly)
+      body.SetMassFromShapes()
+\end{lstlisting}
+
 \subsection{Tesselation}
 Box2D supports only collisions between convex objects. That is why we need to
-breake outlines to convex polygons. There is more ways how to break concave
-objects. We chose Seidel's Triangulation Algorithm implemented by poly2tri
-Python library
-%TODO asi iny algorytmus
-%TODO pridat referenciu na poly2tri
+break outlines to convex polygons. There is more ways how to break concave
+objects. We chose the 2D constrained Delaunay triangulation algorithm
+implemented by poly2tri Python library[\cite{Delauanay}].
 
@@
 Mechanism. This project is also co-financed from the state budget of the Slovak
-Republic..
+Republic.
 

### 2011-02-07 latex/paper.tex
popisana prva cast listingu a teselacia

@@
 image. We convert image to gray scale as seen on line \ref{Detect:grayscale}.
-Then we run histogram equalization (line: \ref{Detect:equalize}).
+Then we run histogram equalization (line:~\ref{Detect:equalize}).
 Equalization makes objects better visible and gives better output for
-thresholding (line: \ref{Detect:threshold}) which makes black and white image
-prepared for outline detection (line: \ref{Detect:contours}).
+thresholding (line:~\ref{Detect:threshold}) which makes black and white image
+prepared for outline detection (line:~\ref{Detect:contours}).
 %TODO Doplnit obrazok s normalizaciou histogramu
@@
 First we have to create boundaries of the world. We define them as vectors from
-bottom left (line: \ref{World:lower}) to top right (line:
+bottom left (line:~\ref{World:lower}) to top right (line:~
 \ref{World:upper}). Objects have to be inside the boundaries, when an object
-touch the boundary it gets stuck. Then we define gravity vector (line:
+touch the boundary it gets stuck. Then we define gravity vector (line:~
 \ref{World:gravity}). The last thing before creation of the world we allow
-objects to sleep(line: \ref{World:sleep}). Object that are not moving fall
+objects to sleep(line:~\ref{World:sleep}). Object that are not moving fall
 asleep, then are ignored by the engine. Last line of Listing \ref{World} creates
@@
 contour tree]
-def CreateObjectsFromCountours(self,cont,h=0,v=0):
+def CreateObjectsFromCountours(self, cont, h=0, v=0):
   if v>0:	%\label{CreateObjects:depth})
@@
 We iterate through contour tree. First level is outer contour of the image
-(Line: \ref{CreateObjects:depth}), because we do not want the outer contour to
-move, we set it as static byt setting density to 0 (Line:
+(line:~\ref{CreateObjects:depth}), because we do not want the outer contour to
+move, we set it as static byt setting density to 0 (line:~
 \ref{CreateObjects:density0}). Every other contour is dynamic body with density
-set to 10 (Line: \ref{CreateObjects:density10}).
+set to 10 (line:~\ref{CreateObjects:density10}).
 
@@
 
-Listing \ref{Objects} shows how to create object from outer contour: 
-\begin{lstlisting}[name=Objects,label=Objects,caption=Creation of object from
+Listings \ref{Objects1},\ref{Objects2},\ref{Objects3} shows how to create object
+from outer contour:
+\begin{lstlisting}[name=Objects,label=Objects1,caption=Creation of object from
 outer contour]
@@
 10m. In that scale is performance of Box2D the best. We are doing it by
-dividing of value of pixel coordinates by 30.0 (Line: \ref{Objects:scaling})
+dividing of value of pixel coordinates by 30.0 (line:~\ref{Objects:scaling})
 
-Then we create a body definition that will represent our contour(Line:
+Then we create a body definition that will represent our contour(line:~
 \ref{Objects:CreateBody}) and set up it initial possition in next line.
 
-After that we create shape of body as chain of edges (Line:
-\ref{Objects:CreateChain}) and assign the array of vertices to it (Line:
+After that we create shape of body as chain of edges (line:~
+\ref{Objects:CreateChain}) and assign the array of vertices to it (line:~
 \ref{Objects:AssignVertices}). Edges are special type of shapes that have no
@@
 
-Listing of the function CreateObject() continous in Listing \ref{Objects}. This
-part of function creates dynamic objects inside the outer contour.
-\begin{lstlisting}[name=Objects,firstnumber=auto,label=Objects,caption=Creation of objecs] if v == 1: try:
+Listing of the function CreateObject() continous in Listing \ref{Objects2}. This
+part of function creates dynamic objects inside the outer contour. In this part
+we prepare list for bodies of objects, so we can modify objects that are already
+created or objects that we want append new shapes.
+\begin{lstlisting}[name=Objects,firstnumber=auto,label=Objects2,caption=Creation of objects] if v == 1:
+    try:
       body = self.objectBodies[h]
@@
       self.objectBodies[h] = body
+\end{lstlisting}
+\subsection{Tesselation}
+Box2D supports only collisions between convex objects and contours of objects
+captured by camera are not convex we have to break outlines to convex polygons.
+There is more ways how to break concave objects. We chose the 2D constrained
+Delaunay triangulation algorithm implemented by poly2tri Python
+library[\cite{Delauanay}]. Function CreateObject() continous in Listing~
+\ref{Objects3}
+\begin{lstlisting}[name=Objects,firstnumber=auto,label=Objects3,caption=Creation
+ of objects]
     polyline = []
     for (x,y) in cont:
-      polyline.append(p2t.Point(x,y))
-    cdt = p2t.CDT(polyline)
+      polyline.append(p2t.Point(x,y)) %\label{Objects:polyline})
+    cdt = p2t.CDT(polyline) %\label{Objects:p2t})
     triangles = cdt.triangulate()
@@
       y3 = t.c.y/30.0
-      if math.hypot(x2-x1,y2-y1)<0.1:
+      if math.hypot(x2-x1,y2-y1)<0.1: %\label{Objects:minSize1})
         x2 = x2 + math.copysign(0.1, x2-x1)
         y2 = y2 + math.copysign(0.1, y2-y1)
-        print "kratky vektor"
       if math.hypot(x3-x2,y3-y2)<0.1:
@@
         y3 = y3 + math.copysign(0.1, y3-y2)
-        print "kratky vektor"
       if math.hypot(x1-x3,y1-y3)<0.1:
         x1 = x1 + math.copysign(0.1, x1-x3)
-        y1 = y1 + math.copysign(0.1, y1-y3)
-        print "kratky vektor"
-      poly=box2d.b2PolygonDef()
+        y1 = y1 + math.copysign(0.1, y1-y3) %\label{Objects:minSize2})
+      poly=box2d.b2PolygonDef()  %\label{Objects:polygondef})
       poly.setVertices(((x1, y1), (x2, y2), (x3, y3)))
@@
       poly.friction = 0.0
-      body.CreateShape(poly)
-      body.SetMassFromShapes()
+      body.CreateShape(poly)  %\label{Objects:createshape})
+      body.SetMassFromShapes() %\label{Objects:setMass})
 \end{lstlisting}
-
-\subsection{Tesselation}
-Box2D supports only collisions between convex objects. That is why we need to
-break outlines to convex polygons. There is more ways how to break concave
-objects. We chose the 2D constrained Delaunay triangulation algorithm
-implemented by poly2tri Python library[\cite{Delauanay}].
+Objects:polyline
+Objects:p2t
+Objects:minSize1
+Objects:minSize2
+Objects:polygondef
+Objects:createshape
+Objects:setMass
 

### 2011-02-08 latex/paper.tex
dopisany obsah, okrem futere work a abstractu

@@
 \usepackage{url}
+\usepackage{graphicx}
 \usepackage{natbib}
@@
 \begin{frontmatter}
-\title{Simulation of 2D physics of hand drawn objects using OpenCV and Box2D}
+\title{Simulation of 2D physics of objects captured by web camera using OpenCV
+and Box2D}
 \author[Bratislava]{Michal Sedlák}
@@
 camera for new image. Then as we see in \ref{Capture:query} we can get the
-image from camera and store it in the variable named image. Now when we have
+image from camera and store it in the variable named image. Capured image
+is shown in Figure \ref{fig:captured}.
+
+\begin{figure}[h]
+\includegraphics[width=\columnwidth]{images/1test.png}
+\caption{Image captured form camera}
+\label{fig:captured}
+\end{figure}
+
+Now when we have
 image data stored in the variable, we can process data to find outlines.
@@
 image. We convert image to gray scale as seen on line \ref{Detect:grayscale}.
-Then we run histogram equalization (line:~\ref{Detect:equalize}).
-Equalization makes objects better visible and gives better output for
-thresholding (line:~\ref{Detect:threshold}) which makes black and white image
-prepared for outline detection (line:~\ref{Detect:contours}).
-%TODO Doplnit obrazok s normalizaciou histogramu
-%TODO Doplnit obrazok s thresholdom
+
+Then we run histogram equalization (line:~\ref{Detect:equalize}). Equalization
+makes objects better visible and gives better output for thresholding
+(line:~\ref{Detect:threshold}) which makes black and with image prepared for outline detection (line:~\ref{Detect:contours}). Output
+of thresholding is shown in (Figure \ref{fig:threshold}).
+
+\begin{figure}[h]
+\includegraphics[width=\columnwidth]{images/3test-equalize-histogram.png}
+\caption{Image after histogram equalization}
+\label{fig:histogram}
+\end{figure}
+
+\begin{figure}[h]
+\includegraphics[width=\columnwidth]{images/4test-threshold.png}
+\caption{Image after thresholding}
+\label{fig:threshold}
+\end{figure}
+
 After outline detection we have tree of contours stored in the variable
@@
 objects, that is why we use polynomial approximation of the contour points.
-(line:~\ref{Detect:approx}).
+(line:~\ref{Detect:approx}). Visualusation of outlines is shown in Figure:
+\ref{fig:contours}.
+
+\begin{figure}[h]
+\includegraphics[width=\columnwidth]{images/5test-contours.png}
+\caption{Visualisation of contours}
+\label{fig:contours}
+\end{figure}
 
@@
 objects and apply a physics.
-%TODO Doplnit obrazok so zvyraznenymi outlineami
 
@@
     triangles = cdt.triangulate()
-    for t in triangles:
+    for t in triangles:  %\label{Objects:scale1})
       x1 = t.a.x/30.0
@@
       x3 = t.c.x/30.0
-      y3 = t.c.y/30.0
+      y3 = t.c.y/30.0  %\label{Objects:scale2})
       if math.hypot(x2-x1,y2-y1)<0.1: %\label{Objects:minSize1})
@@
 \end{lstlisting}
-Objects:polyline
-Objects:p2t
-Objects:minSize1
-Objects:minSize2
-Objects:polygondef
-Objects:createshape
-Objects:setMass
+The creation of objects continues with tesselation. We need to assigne vertices
+to structure that could be understood by poly2tri library
+(line:~\ref{Objects:polyline}) and we initialize the CDT object
+(line:~\ref{Objects:p2t}). In next line we call function that will create
+triangles from the verteces assigned before. These triangles are in image pixel
+coordinates, so we need to scale them at first
+(lines:~\ref{Objects:scale1}-\ref{Objects:scale2}). Now when we have triangles
+scaled we need to scale the triangles that are too small to triangles with size
+at least 0.1m because of speed optimalization, this is done in
+lines:~\ref{Objects:minSize1}-\ref{Objects:minSize2}). Now we have set of
+tirangular shapes that could be attached to body
+(line:~\ref{Objects:createshape:}). Because these objects are compound objects,
+we need to set the mass center and ammount to this body. We can let Box2D set
+this properties based on shape information with body function
+SetMassFromShapes() (line:~\ref{Objects:setMass}). Visualisation of objects is
+in Figure ref{fig:objects}
 
-\subsection{Implementation}
-%TODO dat sem zdrojovy kod a popisat ho
+\begin{figure}[h]
+\includegraphics[width=\columnwidth]{images/6dynamic-objets.png}
+\caption{Visualisation of objects after triangulation}
+\label{fig:objects}
+\end{figure}
+
+After this we can add other objects and start simulation by function Step().
+After few second of simulation are all objects on the bottom of the screen like
+in Figure \ref{fig:simulation}.
+
+\begin{figure}[h]
+\includegraphics[width=\columnwidth]{images/7dynamic-objets-simulation.png}
+\caption{Visualisation of simulation}
+\label{fig:simulation}
+\end{figure}
+
 \section{Future work}

### 2011-02-09 latex/paper.tex
posledn verzia pred korekciami

@@
 \usepackage{color}
+\usepackage{subfig}
+
+%nastavenie vypisov kodu
 \usepackage{listings}
-\lstset{ %
+\usepackage{caption}
+
+\captionsetup[lstlisting]{singlelinecheck=false}
+
+\lstnewenvironment{code}[1][]%
+  {\minipage{\columnwidth} 
+   \lstset{
 language=Python, 
@@
 numberstyle=\tiny,
-xleftmargin= 10pt,
+xleftmargin= 12pt,
+abovecaptionskip=10pt,
 stepnumber=1,
 numbersep=5pt,
-backgroundcolor=\color{white}, 
-showspaces=false,
-showstringspaces=false,
-showtabs=false,
+frame=none,
+tabsize=2,
+captionpos=b,
+breaklines=true,
+breakatwhitespace=false,
+escapeinside={\%}{)}
+}
+}
+  {\endminipage}
+
+\lstset{
+language=Python, 
+basicstyle=\footnotesize,
+numbers=left,
+numberstyle=\tiny,
+xleftmargin= 12pt,
+abovecaptionskip=10pt,
+stepnumber=1,
+numbersep=5pt,
 frame=none,
@@
 \begin{abstract}
-%TODO Napisat abstrakt
-
+The paper presents one approach to simulation of physics applied on objects
+captured by web camera. Introduced approach utilise OpenCV library for image
+capturing and contour detection. Objects detected by OpenCV are reconstructed
+from its outlines in Box2D environment so the physics can be applied to it.
+Because of restrictions of Box2D we needed to do approximation and scaling of
+outlines and tessellation of objects with Delaunay triangulation algorithm.
 \end{abstract}
 \begin{keyword}
-Maximum 5 keywords.
+OpenCV, Python, Box2D, physics, tessellation
 \end{keyword}
@@
 
-Simple image capture is shown in Listing \ref{Capture}.
+Simple image capture is shown in Listing~\ref{Capture}.
 \begin{lstlisting}[caption=Query image frame from web camera, label=Capture]
@@
 \end{lstlisting}
-In line \ref{Capture:init} of listing \ref{Capture} we initialize our web
+In line \ref{Capture:init} of Listing~\ref{Capture} we initialize our web
 camera. In variable camera is allocated and initialized object that can query
 camera for new image. Then as we see in \ref{Capture:query} we can get the
-image from camera and store it in the variable named image. Capured image
+image from camera and store it in the variable named image. Captured image
 is shown in Figure \ref{fig:captured}.
-
 \begin{figure}[h]
-\includegraphics[width=\columnwidth]{images/1test.png}
+\center
+\includegraphics[width=0.8\columnwidth]{images/1test.png}
 \caption{Image captured form camera}
@@
 
-Now when we have
-image data stored in the variable, we can process data to find outlines.
+Now when we have image data stored in the variable, we can process data to find
+outlines.
+
 \begin{lstlisting}[caption=Outline detection, label=Detect]
@@
 \end{lstlisting}
-In function in Listing \ref{Detect} is shown how to find outlines of objects in
-image. We convert image to gray scale as seen on line \ref{Detect:grayscale}.
+
+In function in Listing~\ref{Detect} is shown how to find outlines of objects in
+image. We convert image to grey scale as seen on line \ref{Detect:grayscale}.
 
@@
 makes objects better visible and gives better output for thresholding
-(line:~\ref{Detect:threshold}) which makes black and with image prepared for outline detection (line:~\ref{Detect:contours}). Output
-of thresholding is shown in (Figure \ref{fig:threshold}).
+(line:~\ref{Detect:threshold}) which makes black and with image prepared for
+outline detection (line:~\ref{Detect:contours}). Output of thresholding is
+shown in (Figure \ref{fig:threshold}).
 
 \begin{figure}[h]
-\includegraphics[width=\columnwidth]{images/3test-equalize-histogram.png}
-\caption{Image after histogram equalization}
+  \center
+  \subfloat[Equalize histogram]{
     \label{fig:histogram}
-\end{figure}
-
-\begin{figure}[h]
-\includegraphics[width=\columnwidth]{images/4test-threshold.png}
-\caption{Image after thresholding}
+    \includegraphics[width=0.48\columnwidth]{images/3test-equalize-histogram.png}
+  }
+  \subfloat[Thresholding]{
     \label{fig:threshold}
+    \includegraphics[width=0.48\columnwidth]{images/4test-threshold.png}
+   }
+\caption{Effects applied on images}
+\label{fig:operations}
 \end{figure}
@@
 objects, that is why we use polynomial approximation of the contour points.
-(line:~\ref{Detect:approx}). Visualusation of outlines is shown in Figure:
+(line:~\ref{Detect:approx}). Visualisation of outlines is shown in Figure:
 \ref{fig:contours}.
@@
 \begin{figure}[h]
-\includegraphics[width=\columnwidth]{images/5test-contours.png}
+\center
+\includegraphics[width=0.8\columnwidth]{images/5test-contours.png}
 \caption{Visualisation of contours}
@@
 implementation of physics, or use one of commercial or open source engines. We
-chose Box2D[\cite{GameEngines}], which is open source 2D physiscs engine with
+chose Box2D[\cite{GameEngines}], which is open source 2D physics engine with
 possibility to simulate rigid body objects and their collisions.
@@
 objects to sleep(line:~\ref{World:sleep}). Object that are not moving fall
-asleep, then are ignored by the engine. Last line of Listing \ref{World} creates
+asleep, then are ignored by the engine. Last line of Listing~\ref{World} creates
 the world.
@@
 contours.
-\subsubsection{Contour tree}
+\subsection{Contour tree}
 Contour tree is object in which are stored points of each contour. Contours are
@@
 (line:~\ref{CreateObjects:depth}), because we do not want the outer contour to
-move, we set it as static byt setting density to 0 (line:~
+move, we set it as static by setting density to 0 (line:~
 \ref{CreateObjects:density0}). Every other contour is dynamic body with density
@@
 shapes for our contours.
-\subsubsection{Bodies, shapes and collisions}
+\subsection{Bodies, shapes and collisions}
 Bodies are backbone used by shapes. One body can contain more shapes, but one
@@
 Then we create a body definition that will represent our contour(line:~
-\ref{Objects:CreateBody}) and set up it initial possition in next line.
+\ref{Objects:CreateBody}) and set up it initial position in next line.
 
@@
 \ref{Objects:AssignVertices}). Edges are special type of shapes that have no
-mass, is represented as line betven vertices that collide with other non-edge
+mass, is represented as line between vertices that collide with other non-edge
 objects. Edges are easy to create because they do not have to be concave unlike
@@
 Box2D does not keep track about body definitions, we have to store bodies in to
-array for later use\ref{Objects:CountourBodies}.
+array for later use (line: \ref{Objects:CountourBodies}).
 
-Listing of the function CreateObject() continous in Listing \ref{Objects2}. This
+Listing of the function CreateObject() continuous in Listing~\ref{Objects2}. This
 part of function creates dynamic objects inside the outer contour. In this part
@@
 \end{lstlisting}
-\subsection{Tesselation}
+\subsection{tessellation}
 Box2D supports only collisions between convex objects and contours of objects
@@
 Delaunay triangulation algorithm implemented by poly2tri Python
-library[\cite{Delauanay}]. Function CreateObject() continous in Listing~
+library[\cite{Delauanay}]. Function CreateObject() continuous in Listing~
 \ref{Objects3}
@@
 \end{lstlisting}
-The creation of objects continues with tesselation. We need to assigne vertices
+The creation of objects continues with tessellation. We need to assign vertices
 to structure that could be understood by poly2tri library
@@
 (line:~\ref{Objects:p2t}). In next line we call function that will create
-triangles from the verteces assigned before. These triangles are in image pixel
+triangles from the vertices assigned before. These triangles are in image pixel
 coordinates, so we need to scale them at first
@@
 lines:~\ref{Objects:minSize1}-\ref{Objects:minSize2}). Now we have set of
-tirangular shapes that could be attached to body
+triangular shapes that could be attached to body
 (line:~\ref{Objects:createshape:}). Because these objects are compound objects,
-we need to set the mass center and ammount to this body. We can let Box2D set
+we need to set the center of mass and amount to this body. We can let Box2D set
 this properties based on shape information with body function
 SetMassFromShapes() (line:~\ref{Objects:setMass}). Visualisation of objects is
-in Figure ref{fig:objects}
+in Figure \ref{fig:objects}.
 
@@
 
-After this we can add other objects and start simulation by function Step().
+After this we can add other objects and start simulation by function \lstinline{Step()}.
 After few second of simulation are all objects on the bottom of the screen like
-in Figure \ref{fig:simulation}.
+is shown in figure \ref{fig:simulation}.
 
@@
 \section{Future work}
-Identifikacia objektov
-Sledovanie objektov a morfing 
-Interakcia hybucich sa objektov zachytenych kamerov s Box2D reprezentaciou
+This approach can be used in interactive blackboards used for education of
+physics on elementary schools, in future work we plan to implement
+identification of some special objects like springs or joints.
+
+We are planning to implement object tracking, and dynamic object morphing so we
+could interact with simulated objects. Because of Box2D is rigid body engine,
+is complicated to simulate physics of objects that change their shape in time.
+We plan to implement some soft body elements to make this possible.
+
+The last stage will be usage of captured images as source of textures of
+simulated objects. Because this is only decorative element, we are planning to
+implement this task as a last one.
 

### 2011-02-09 latex/paper.tex
finalna verzia

@@
 \documentclass{ifacconf}
-\usepackage[english]{babel}
 \usepackage[T1]{fontenc}
@@
 
-\lstnewenvironment{code}[1][]%
-  {\minipage{\columnwidth} 
 \lstset{
@@
 breaklines=true,
-breakatwhitespace=false,
-escapeinside={\%}{)}
-}
-}
-  {\endminipage}
-
-\lstset{
-language=Python, 
-basicstyle=\footnotesize,
-numbers=left,
-numberstyle=\tiny,
-xleftmargin= 12pt,
-abovecaptionskip=10pt,
-stepnumber=1,
-numbersep=5pt,
-frame=none,
-tabsize=2,
-captionpos=b,
-breaklines=true,
-breakatwhitespace=false,
+breakatwhitespace=true,
 escapeinside={\%}{)}
@@
 \section{Introduction}
-This paper describes applying of Newtonian physics to hand drawn objects
-recognized in image from camera. Simulation of physics is used in many modern
-applications. You can find in implementations used by 3D drawing and animation
-programs, more complex used in game engines or exact and precise simulation in
-CAE programs. Paper describes process of animation of hand drawn object, from a
-capturing phase, over recognition of the objects, interpretation objects in
+This paper describes applying of Newtonian physics to objects
+recognized in image captured from camera. Simulation of physics is used in many
+modern applications. You can find it in implementations used by game
+engines, there are as well more complex implementation used in 3D drawing and
+animation programs or exact and precise simulation in CAE and CAD programs.
+Paper describes process of animation of objects, from a capturing
+phase, over detection of the object outlines and interpretation of objects in 
 physical engine, to animation of such objects. This approach can be applied in
@@
 objects from image. We have used a web camera as a source and Open Computer
-Vision library as processing tool of the images.
+Vision (OpenCV) library as processing tool of the images.
 
@@
 programming functions for real time computer vision, with more than five hundred
-optimized algorithms. It can be used with C++, C and Python. We chose Python for
-implementation in our application.
+optimized algorithms. It can be used with C++, C and Python. We chose Python
+version, which is optimized Python wrapper to C++ functions.
 
-Simple image capture is shown in Listing~\ref{Capture}.
+In the beginning we have to capture image to work with. OpenCV library has
+implemented methods for image capture from camera. Simple image capture is shown
+in Listing~\ref{Capture}.
+
 \begin{lstlisting}[caption=Query image frame from web camera, label=Capture]
@@
 \end{lstlisting}
+
 In line \ref{Capture:init} of Listing~\ref{Capture} we initialize our web
-camera. In variable camera is allocated and initialized object that can query
-camera for new image. Then as we see in \ref{Capture:query} we can get the
-image from camera and store it in the variable named image. Captured image
-is shown in Figure \ref{fig:captured}.
+camera. In variable \lstinline{camera} is allocated and initialized object that
+can query web camera for new image. Then as we see in Listing~\ref{Capture}
+line~\ref{Capture:query} we can get the image from camera and store it in the
+variable named \lstinline{image}. Captured image is shown in
+Fig.~\ref{fig:captured}.
+
 \begin{figure}[h]
@@
 
-In function in Listing~\ref{Detect} is shown how to find outlines of objects in
-image. We convert image to grey scale as seen on line \ref{Detect:grayscale}.
+In function \lstinline{DetectOutline()} in Listing~\ref{Detect} is shown how to
+find outlines of objects in image.
+First we convert image to grey scale as seen on Listing~\ref{Detect},
+line~\ref{Detect:grayscale}.
 
-Then we run histogram equalization (line:~\ref{Detect:equalize}). Equalization
-makes objects better visible and gives better output for thresholding
-(line:~\ref{Detect:threshold}) which makes black and with image prepared for
-outline detection (line:~\ref{Detect:contours}). Output of thresholding is
-shown in (Figure \ref{fig:threshold}).
+Then we run histogram equalization (Listing~\ref{Detect},
+line~\ref{Detect:equalize}). Equalization makes objects better visible and gives
+better output for thresholding (Listing~\ref{Detect},
+line:~\ref{Detect:threshold}) which makes black and white as you can see in
+Fig.~\ref{fig:histogram}.
+
+Outline detection is done with function
+\lstinline{cv.FindContours()} (Listing~\ref{Detect},
+line:~\ref{Detect:contours}). Output of thresholding is shown in
+Fig.~\ref{fig:threshold}.
 
@@
 
-After outline detection we have tree of contours stored in the variable
-self.contours. These trees are iterable objects sorted from outer to inner
-outline connected by property h\_next and v\_next that we will describe in
+After outline detection we have a tree of contours stored in the variable
+\lstinline{self.contours}. These trees are iterable objects sorted from outer to
+inner outline connected by property h\_next and v\_next that we will describe in
 paragraph about creation of objects from outlines.
 
-Contour can be very complicated and consist of thousands of points, which could
-cause too complicated objects. It is time demanding to simulate complicated
-objects, that is why we use polynomial approximation of the contour points.
-(line:~\ref{Detect:approx}). Visualisation of outlines is shown in Figure:
-\ref{fig:contours}.
+Contour can be very complicated and consist of thousands of points, which
+would cause objets with thousands of vertices. It is time demanding to
+simulate complicated objects, that is why we use polynomial approximation of
+the contour points. (line:~\ref{Detect:approx}). Visualisation of outlines is
+shown in Fig.~\ref{fig:contours}.
 
@@
 There is lot of physics engines that can be used for simulation of physics.
-Because we wanted to simulate physics only in 2D we could, code our own
+Because we wanted to simulate physics only in 2D we could code our own
 implementation of physics, or use one of commercial or open source engines. We
-chose Box2D[\cite{GameEngines}], which is open source 2D physics engine with
-possibility to simulate rigid body objects and their collisions.
+chose Box2D [\cite{GameEngines}], which is open source 2D physics engine with
+implementation of rigid body objects and their collisions.
 \subsection{World}
@@
 First we have to create boundaries of the world. We define them as vectors from
-bottom left (line:~\ref{World:lower}) to top right (line:~
-\ref{World:upper}). Objects have to be inside the boundaries, when an object
-touch the boundary it gets stuck. Then we define gravity vector (line:~
-\ref{World:gravity}). The last thing before creation of the world we allow
-objects to sleep(line:~\ref{World:sleep}). Object that are not moving fall
-asleep, then are ignored by the engine. Last line of Listing~\ref{World} creates
-the world.
+bottom left (Listing~\ref{World}, line:~\ref{World:lower}) to top right
+(Listing~\ref{World}, line:~\ref{World:upper}). Objects have to be inside the
+boundaries, when an object touch the boundary it gets stuck. Then we define
+gravity vector (Listing~\ref{World}, line:~\ref{World:gravity}). The last
+thing before creation of the world we allow objects to
+sleep (Listing~\ref{World}, line:~\ref{World:sleep}). Object that are not moving
+fall asleep, then they are ignored by the engine. Last line of
+Listing~\ref{World} creates the world.
 
 World is created and we are ready to create objects from outlines.
+
 \subsection{Objects}
 Every object that is simulated in Box2D consists of body and shapes. Our objects
-are described by the contour tree. To create objects we need to iterate contour
-tree, find contours that belongs to together and create objects for these
-contours.
+are described by the contour tree. To create objects we need to iterate
+through contour tree to find contours that belongs together and create
+objects for these contours.
+
 \subsection{Contour tree}
 Contour tree is object in which are stored points of each contour. Contours are
-connected by functions returning reference to other contours with h\_next() and
-v\_next(). h\_next() is referencing to deeper contour, and v\_next is
-referencing to another object contour. To iterate over all contours we have
-created recursive function shown in Listing: \ref{CreateObjects}.
-\begin{lstlisting}[label=CreateObjects,caption=Function to iterate through
-contour tree]
+connected by functions returning reference to other contours with
+\lstinline{h_next()} and \lstinline{v_next()}, where \lstinline{h_next()} is
+reference to deeper contour, and \lstinline{v_next()} is reference to another
+object contour. To iterate over all contours we have created recursive function
+shown in Listing: \ref{CreateObjects}.
+
+\begin{lstlisting}[label=CreateObjects,caption=Function to iterate through contour tree]
 def CreateObjectsFromCountours(self, cont, h=0, v=0):
@@
     v += 1
-    self.CreateObjectsFromCountours(cont.v_next(),h,v)
+    self.CreateObjectsFromCountours( cont.v_next(), h, v)
     v -= 1
@@
     h += 1
-    self.CreateObjectsFromCountours(cont.h_next(),h,v)
+    self.CreateObjectsFromCountours( cont.h_next(), h, v)
 \end{lstlisting}
+
 We iterate through contour tree. First level is outer contour of the image
-(line:~\ref{CreateObjects:depth}), because we do not want the outer contour to
-move, we set it as static by setting density to 0 (line:~
-\ref{CreateObjects:density0}). Every other contour is dynamic body with density
-set to 10 (line:~\ref{CreateObjects:density10}).
+(Listing \ref{CreateObjects} line:~\ref{CreateObjects:depth}), because we do not
+want the outer contour to move, we set it as static by setting density to 0
+(Listing \ref{CreateObjects} line:~ \ref{CreateObjects:density0}). Every other
+contour is dynamic body with density set to 10 (Listing \ref{CreateObjects}
+line:~\ref{CreateObjects:density10}).
 
@@
 have position and velocity. Forces, torques and impulses can be applied to body
-[\cite{Box2DManual}].  Bodies just hold the shapes. Shapes are elements that
+[\cite{Box2DManual}]. Bodies just hold the shapes and shapes are elements that
 collide together.
 
-Listings \ref{Objects1},\ref{Objects2},\ref{Objects3} shows how to create object
-from outer contour:
-\begin{lstlisting}[name=Objects,label=Objects1,caption=Creation of object from
-outer contour]
+Listings \ref{Objects1},\ref{Objects2},\ref{Objects3} shows process of object
+creation:
+\begin{lstlisting}[name=Objects,label=Objects1,caption=Creation of object from outer contour]
 def CreateObject(self, cont, h,v):
@@
 10m. In that scale is performance of Box2D the best. We are doing it by
-dividing of value of pixel coordinates by 30.0 (line:~\ref{Objects:scaling})
+dividing of value of pixel coordinates by 30.0
+(Listing~\ref{Objects1} line:~\ref{Objects:scaling})
 
-Then we create a body definition that will represent our contour(line:~
-\ref{Objects:CreateBody}) and set up it initial position in next line.
+Then we create a body definition that will represent our 
+contour(Listing~\ref{Objects1} line:~ \ref{Objects:CreateBody}) and set up it
+initial position in next line.
 
-After that we create shape of body as chain of edges (line:~
-\ref{Objects:CreateChain}) and assign the array of vertices to it (line:~
-\ref{Objects:AssignVertices}). Edges are special type of shapes that have no
-mass, is represented as line between vertices that collide with other non-edge
-objects. Edges are easy to create because they do not have to be concave unlike
-polygons.
+After that we create shape of body as chain of edges (Listing~\ref{Objects1}
+line:~ \ref{Objects:CreateChain}) and assign the array of vertices to it
+(Listing~\ref{Objects1} line:~ \ref{Objects:AssignVertices}). Edges are special
+type of shapes that have no mass. Edges are represented as lines between
+vertices that collide with other non-edge objects. Edges are easy to create
+because they do not have to be concave unlike polygons.
 
-At last we attach this shape to created body \ref{Objects:AttachShape}. Because
-Box2D does not keep track about body definitions, we have to store bodies in to
-array for later use (line: \ref{Objects:CountourBodies}).
+At last we attach this shape to created body Listing~\ref{Objects1}
+\ref{Objects:AttachShape}. Because Box2D does not keep track about body
+definitions, we have to store bodies in to array for later use
+(Listing~\ref{Objects1} line: \ref{Objects:CountourBodies}).
 
-Listing of the function CreateObject() continuous in Listing~\ref{Objects2}. This
-part of function creates dynamic objects inside the outer contour. In this part
-we prepare list for bodies of objects, so we can modify objects that are already
-created or objects that we want append new shapes.
-\begin{lstlisting}[name=Objects,firstnumber=auto,label=Objects2,caption=Creation of objects] if v == 1:
+Listing of the function \lstinline{CreateObject()} continues in
+Listing~\ref{Objects2}. This part of function creates dynamic objects inside the
+outer contour. In this part we prepare list for bodies of objects, so we can
+modify objects that are already created or objects that we want append new shapes.
+
+\begin{lstlisting}[name=Objects,firstnumber=auto,label=Objects2,caption=Creation of objects]
+if v == 1:
     try:
@@
 \end{lstlisting}
+
 \subsection{tessellation}
 Box2D supports only collisions between convex objects and contours of objects
-captured by camera are not convex we have to break outlines to convex polygons.
-There is more ways how to break concave objects. We chose the 2D constrained
-Delaunay triangulation algorithm implemented by poly2tri Python
-library[\cite{Delauanay}]. Function CreateObject() continuous in Listing~
-\ref{Objects3}
-\begin{lstlisting}[name=Objects,firstnumber=auto,label=Objects3,caption=Creation
- of objects]
+captured by camera are mostly not convex. So we have to break outlines to
+convex polygons. There is more ways how to break concave objects. We chose the
+2D constrained Delaunay triangulation algorithm implemented by poly2tri Python
+library[\cite{Delauanay}]. Function CreateObject() continuous in
+Listing~\ref{Objects3}
+
+\begin{lstlisting}[name=Objects,firstnumber=auto,label=Objects3,caption=Creation of objects]
     polyline = []
@@
 \end{lstlisting}
+
 The creation of objects continues with tessellation. We need to assign vertices
 to structure that could be understood by poly2tri library
-(line:~\ref{Objects:polyline}) and we initialize the CDT object
-(line:~\ref{Objects:p2t}). In next line we call function that will create
-triangles from the vertices assigned before. These triangles are in image pixel
-coordinates, so we need to scale them at first
-(lines:~\ref{Objects:scale1}-\ref{Objects:scale2}). Now when we have triangles
-scaled we need to scale the triangles that are too small to triangles with size
-at least 0.1m because of speed optimalization, this is done in
-lines:~\ref{Objects:minSize1}-\ref{Objects:minSize2}). Now we have set of
-triangular shapes that could be attached to body
-(line:~\ref{Objects:createshape:}). Because these objects are compound objects,
-we need to set the center of mass and amount to this body. We can let Box2D set
-this properties based on shape information with body function
-SetMassFromShapes() (line:~\ref{Objects:setMass}). Visualisation of objects is
-in Figure \ref{fig:objects}.
+(Listing~\ref{Objects3} line:~\ref{Objects:polyline}) and we initialize the CDT
+object (Listing~\ref{Objects3} line:~\ref{Objects:p2t}). In next line we call
+function that will create triangles from the vertices assigned before. These
+triangles are in image pixel coordinates, so we need to scale them at first
+(Listing~\ref{Objects3} lines:~\ref{Objects:scale1}-\ref{Objects:scale2}). Now
+when we have triangles scaled we need to scale the triangles that are too small
+to triangles with size at least 0.1m because of speed optimalization, this is done in
+Listing~\ref{Objects3} lines:~\ref{Objects:minSize1}-\ref{Objects:minSize2}).
+Now we have set of triangular shapes that could be attached to body
+(Listing~\ref{Objects3} line:~\ref{Objects:createshape}). Because these objects
+are compound objects, we need to set the center and amount of mass to this 
+body. We can let Box2D set this properties based on shape information with
+function \lstinline{SetMassFromShapes()} (Listing~\ref{Objects3}
+line:~\ref{Objects:setMass}). Visualisation of objects is in Fig.~\ref{fig:objects}.
 
@@
 After few second of simulation are all objects on the bottom of the screen like
-is shown in figure \ref{fig:simulation}.
+is shown in Fig~\ref{fig:simulation}.
 
